From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-11-11 paper.tex
[minor] formatting

Looking at techniques that both operate on-line and have been deployed in field
experiments, one finds that most approaches rely on head pose estimation alone
(no eye gaze tracking) and are generally based on depth sensors (RGB-D) .
Fanelli~\etal provides an overview of these approaches
in~\cite{fanelli2012real}, and recent examples include~\cite{baxter2014tracking,
anzalone}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{head_pose}
    \caption{The 6D head pose is estimated by fitting a 3D model of an
        adult head (left) {\it\sc[FACE REDACTED FOR REVIEW]} onto the detected 2D features of the face (right). We
        rely on an iterative $PnP$ algorithm, using 8 correspondence pairs
        (three are depicted: the sellion -- the nasal depression --, the left
        tragion and the menton). The 3D origin of the head is set at the sellion.}

    \label{head_pose}
\end{figure}

>>>>

Looking at techniques that both operate on-line and have been deployed in field
experiments, one finds that most approaches rely on head pose estimation alone
(no eye gaze tracking) and are generally based on depth sensors (RGB-D).
Fanelli~\etal provides an overview of these approaches
in~\cite{fanelli2012real}, and recent examples include~\cite{baxter2014tracking,
anzalone}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{head_pose}
    \caption{The 6D head pose is estimated by fitting a 3D model of an
        adult head (left) {\it\sc[FACE REDACTED FOR REVIEW]} onto the detected 2D features of the face (right). We
        rely on an iterative $PnP$ algorithm, using 8 correspondence pairs
        (three are depicted: the sellion -- the nasal depression --, the left
        tragion and the menton). The 3D origin of the head is set at the sellion.}
\label{head_pose}
\end{figure}
